A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-06-05 introduction.tex
Satisfying assignment

\cref{const:x-in-c-dd,const:y-in-b,const:x-substring} can be translated to the
product of Parikh automata $B \times A'$, where $A'$ (\cref{fig:aut_a}) is the
Parikh automata obtained by applying the encoding of $\Substring$ described in
\cite{ostrich-plus}. That description can then be used to obtain values for
$\CountOf{\Char{a}}(y)$ and $\CountOf{\Char{b}}(y)$. Here follows an intuition
for our method on $B \times A'$ under the global constraint
\cref{const:more-a-than-b}. Note that the cost registers of \cref{fig:aut_b} are
simply counting letters, while the extra registers $l, r$ in $A'$ also keeps
track of the matched substring. However, these registers can be mostly
disregarded here, since we have no constraints on their values.

>>>>

Intuitively, we see that the constraints are satisfiable.
\cref{const:more-a-than-b} implies that the starting offset must be either $1$
or $2$, that is we need to fill out $y$ with either one or two symbols before
the substring $x$ starts. The state $D$ is dead, as $B$ contains no transitions
with label $\Char{d}$, and hence none of the transitions into $D$ can appear in
the intersection of the languages. An example satisfying assignment is $y =
\Char{acca}$, which gives $x = \Char{c}$, $i = 1$, $n = 1$, but others are
possible.

To solve \cref{ex:string-constraints} using \Calculus{},
\cref{const:x-in-c-dd,const:y-in-b,const:x-substring} can be translated to the
product of Parikh automata $B \times A'$, where $A'$ (\cref{fig:aut_a}) is the
Parikh automata obtained by applying the encoding of $\Substring$ described in
\cite{ostrich-plus}. That description can then be used to obtain values for
$\CountOf{\Char{a}}(y)$ and $\CountOf{\Char{b}}(y)$. Here follows an intuition
for our method on $B \times A'$ under the global constraint
\cref{const:more-a-than-b}. Note that the cost registers of \cref{fig:aut_b} are
simply counting letters, while the extra registers $l, r$ in $A'$ also keeps
track of the matched substring. However, these registers can be mostly
disregarded here, since we have no constraints on their values.
